%!TEX program = xelatex

\immediate\write18{makeindex -s nomencl.ist -o "\jobname.nls" "\jobname.nlo"}

\documentclass{Classes/UITBA}
%\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}

\usepackage{algorithm} 
\usepackage{tabularx}  
\usepackage{cuted}  
\usepackage[utf8]{inputenc}
\usepackage{libertine}
\usepackage[algo2e]{algorithm2e}
\usepackage{graphicx}
\usepackage{float}
\usepackage{textcmds}
\newtheorem{mydef}{Definition}


%\include{Preamble/Premable}
% \selectlanguage{vietnamese}
\begin{document}


%\begin{otherlanguage}{vietnamese} %Uncomment this line and its corresponding ending line if \selectlanguage{english}

\pagestyle{empty}
\newgeometry{left=3cm,right=3cm,top=3cm,bottom=3cm}
%\include{Cover/Cover}
\clearpage
\restoregeometry

%\include{TheBoard/TheBoard}
%\include{Acknowledgement/Acknowledgement}
%\include{Comment/Comment}
%\end{otherlanguage}

\pagestyle{empty}
% \include{Cover/Cover}
\include{Conference/Conference}
\include{Acknowledgement/Acknowledgement}

\renewcommand{\contentsname}{Mục lục\centering}
\tableofcontents
\renewcommand{\listfigurename}{Danh mục hình\centering}
\listoffigures
\renewcommand{\listtablename}{Danh mục bảng\centering}
\listoftables
%\renewcommand{\nomname}{\IfLanguageName{vietnamese}{Danh sách các từ viết tắt}{Abbreviations}}
%\printnomenclature[2cm]
 
\clearpage
\pagestyle{plain}
\setcounter{page}{1}


\newgeometry{left=3.5cm,right=2cm,top=3cm,bottom=3.5cm}

\include{Abstract/Abstract}

\include{Chapter1/Chapter1}
\include{Chapter2/Chapter2}
\include{Chapter3/Chapter3}
\include{Chapter4/Chapter4}
\include{Chapter5/Chapter5}
\include{Chapter6/Chapter6}


% \include{Reference/Reference}
% \printbibliography

\begin{thebibliography}{SJL05}

\bibitem{lstmintroduction} N.T.Long. \textit{Giải thích chi tiết về mạng Long Short-Term Memory (LSTM)}. 18 Oct 2018. [Online]. Available: https://nguyentruonglong.net/giai-thich-chi-tiet-ve-mang-long-short-term-memory-lstm.html. [Accessed 23 06 2021].

\bibitem{trashclassification} \textit{Phân loại, thu gom và xử lý rác thải sinh hoạt} [Online]. Available: https://congdongxanh.vn/kinh-nghiem/phan-loai-thu-gom-va-xu-ly-rac-thai-sinh-hoat.html. [Accessed 15 Jun 2021].

\bibitem{trashnet} Gary Thung, Mindy Yang. \textit{Classification of trash for recyclability status}.CS229 Project Report2016, 2016.

\bibitem{lstmprediction1} Liu Yunpeng, Di Hou, Bao Junpeng, Qi Yong. \textit{Multi-step Ahead Time Series Forecasting for Different Data Patterns Based on LSTM Recurrent Neural Network}. 2017 14th Web Information Systems and Applications Conference (WISA). IEEE 2017.

\bibitem{lstmmultistep} Jason Brownlee. \textit{Multi-Step LSTM Time Series Forecasting Models for Power Usage}. 10 Oct 2018. Retrieved from \textit{Deep Learning for Time Series}. [Online]. Available: https://machinelearningmastery.com/how-to-develop-lstm-models-for-multi-step-time-series-forecasting-of-household-power-consumption/

\bibitem{lstmprediction2} XiaoFeng Wang, Ying Zhang. \textit{Multi-Step-Ahead Time Series Prediction Method with Stacking LSTM Neural Network}. 2020 3rd International Conference on Artificial Intelligence and Big Data (ICAIBD). IEEE, 2020.

\bibitem{smartcity} De Carolis, Berardina, Francesco Ladogana, and Nicola Macchiarulo.\textit{YOLO TrashNet: Garbage Detection in Video Streams.} 2020 IEEE Conference on Evolving and Adaptive Intelligent Systems (EAIS). IEEE, 2020.
%\bibitem{DBPedia} Bizer, Christian, Jens Lehmann, Georgi Kobilarov, Sören Auer, Christian Becker, Richard Cyganiak, and Sebastian Hellmann. "DBpedia-A crystallization point for the Web of Data." Web Semantics: science, services and agents on the world wide web 7, no. 3 (2009): 154-165.

\bibitem{lstmprediction3} Bipin Aasi, Syeda Aniqa Imtiaz, Hamzah Arif Qadeer, Magdalean Singarajah, Rasha Kashef. \textit{Stock Price Prediction Using a Multivariate Multistep LSTM: A Sentiment and Public Engagement Analysis Model}. 2021 IEEE International IOT, Electronics and Mechatronics Conference (IEMTRONICS). IEEE, 2021.

\bibitem{thingsboard} 2021 The Thingsboard Authors, \textit{What is ThingsBoard?}, Thingsboard, [Online]. Available: https://thingsboard.io/docs/getting-started-guides/what-is-thingsboard/. [Accessed 22 Jun 2021].

\bibitem{thingsboardapi} Thingsboard team, \textit{ThingsBoard REST API}. Thingsboard. [Online]. Available: http://demo.thingsboard.io/swagger-ui.html.

\bibitem{mapboxapi} Mapbox team, \textit{Mapbox REST API}. Mapbox. [Online]. Available: https://docs.mapbox.com/.

\end{thebibliography}

\end{document}
